Spartanburg 2013 Test Descriptions

### 2014-10-28 Projects/Spartanburg_2013/Spartanburg_2013.tex
Spartanburg 2013: minor update to report

The third test house was a single story, single family residential structure of type 5 construction addressed as 219 Folsom Street. The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.  The burn rooms had a combustible finish comprised of OSB sheets for wall linings.  Two tests were conducted in this structure: 1) Bedroom fire with exterior attack and 2) Living Room fire with exterior attack.

@@

 The third test house was a single story, single family residential structure of type 5 construction addressed as 225 Folsom Street. The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.  The burn rooms had a combustible finish comprised of OSB sheets for wall linings.  One test was conducted in this structure comparing a legacy versus modern sofa with an exterior fire attack.

@@

>>>>

The next test house was a single story, single family residential structure of type 5 construction addressed as 219 Folsom Street. The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.  The burn rooms had a combustible finish comprised of OSB sheets for wall linings.  Two tests were conducted in this structure: 1) Bedroom fire with exterior attack and 2) Living room fire with exterior attack.

@@

 The fifth test house was a single story, single family residential structure of type 5 construction addressed as 225 Folsom Street. The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.  The burn rooms had a combustible finish comprised of OSB sheets for wall linings.  One test was conducted in this structure comparing a legacy versus modern sofa with an exterior fire attack.

@@

  \section{226 Folsom Street}

  The following series of tests were conducted in a single story, single family residential structure of type 5 construction addressed as 226 Folsom Street. The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.  The burns rooms had a combustible finish comprised of OSB sheets for wall linings.  Three tests were conducted in this structure: 1) Wastebasket fire with sprinkler activation, 2) Bedroom fire with exterior attack, and 3) Living room fire with exterior attack.

  \subsection{Test 1: Wastebasket Fire with Sprinkler}

  This fire was ignited in a small wastebasket located between a bed with modern-style mattress and a wooden nightstand in the bedroom of the home near the A/D corner. The windows and door to the room were closed for the duration of the test. The fire grew uninhibited until the sprinkler activated suppressing the fire.  Shortly thereafter, a fire fighting crew made entry to confirm extinguishment.

  Ignition occurred on a modern-style mattress in a bedroom to the rear of the structure near the C/D corner.  The bedroom window on side C of the structure is open during the test as is the interior bedroom doorway. The bedroom window on side D of the structure is closed at the beginning of the test. Fire growth was uninhibited.  The fire in the room of origin grew until the D side window self-vented.  The room of origin reached flashover conditions and the D side window became full exhaust. The adjoining bedroom window on the D side of the structure was vented by the fire fighting crew shortly thereafter. The fire fighting crew then conducted an exterior attack via a single hand-line with a smooth bore nozzle until the fire was extinguished.  Another fire fighting crew made entry into the structure via the Side A door to confirm extinguishment and mop-up.

  \subsection{Test 3: Living Room Fire}

  The fire was ignited on a modern-style sofa in the living room near the A/B corner of the structure.  The A side window to the living room, in addition to the A side front door, were open for the duration of the test. The fire was allowed to grow uninhibited until the fire building reached ventilation-limited conditions.
